---
title: "Untitled"
author: "Kyri Janssen"
date: "2022-11-15"
output: html_document
---

```{r}

library("tidyverse")
library("here")
library(FactoMineR)
library(factoextra)
library(corrplot)
library(ggplot2)
library(ggrepel)
library(ggforce)
library(stringr)
library(sjPlot)
library(janitor)
library(openxlsx)

```
#load in the data and select the variables for the MCA

```{r}
SLR1 <- read_csv2("C:/Users/kmjjanssen/OneDrive - Delft University of Technology/Work/Literature/SLR/Data/SLR_analysis.csv") 

sel1 <- SLR1 %>%
  select(Topic, Type_gentri_new, concept_new, Method_new, Data_ownership_n, Time_data_n, Context_scale, 
         Administrative_category, Unit_new, Extent_movements, Country_NEW, Phase, Segregation, Origin, Destination)



rep_str = c("Residential trajectories of displacees" = "Trajectories of displacees", "Residential trajectories of gentrifiers" = "Trajectories of gentrifiers")

sel1$Topic <- str_replace_all(sel1$Topic, rep_str)
```



# Run MCA 
```{r}
mca1 = MCA(sel1, graph =FALSE)
```

##create dataframes with variables of the dimensions, eigenvalues, and contributions

```{r}

mca1_vars_df = data.frame(mca1$var$coord) #I include the variable name for each category in the last column 
mca1_obs_df = data.frame(mca1$ind$coord) 
mca1_eig_df = data.frame(mca1$eig)
mca1_var_cos2 = data.frame(mca1$var$cos2)
mca1_obs_cos2 = data.frame(mca1$ind$cos2)

```


#Plot variable coordinates in a plot
```{r}


row_names_df_to_remove <- c("Segregation_na", "Origin_na")
mca1_vars_df <- mca1_vars_df[!(row.names(mca1_vars_df) %in% row_names_df_to_remove),]
mca1_var_cos2 <- mca1_var_cos2[!(row.names(mca1_var_cos2) %in% row_names_df_to_remove),]




mca1_vars_df$label <- rownames(mca1_vars_df)


plot_2 <- ggplot(mca1_vars_df, aes(x=Dim.1, y=Dim.2)) + 
  geom_point(position = position_dodge(width = 0.5 )) + 
  geom_vline(xintercept = 0)  + geom_hline(yintercept = 0) +
  geom_label_repel(aes(label = label),box.padding   = 0.2, 
                   size=3, point.padding = 0.2,
                   segment.color = 'grey50', label.size = 0.1, max.overlaps = 15) +
  theme_classic() + theme(legend.position = "none")+
  labs(caption = "MCA out of 48 articles") #+   ggsave("mca1plot3.svg" )


#save_plot(file = "mcaplot.svg", fig = plot1, width = 10, height=8)


plot_2 <- plot_2 + expand_limits(x = c(-2, 3.5), y = c(-2.2, 2.2))

plot_2

```


# perform K-nearest neighbor clustering analysis on the MCA dimensions 
```{r}
mca_vars_num <- mca1_vars_df %>%
  select(Dim.1, Dim.2)


k2_1 <- kmeans(mca_vars_num, centers = 3, nstart=25)


```

# calculate standard deviation of the clusters

```{r}
clusters <- k2_1$cluster
centers <- k2_1$centers


res_sd <- NULL
for (cl in c(unique(clusters))){
    df_part <- mca_vars_num[clusters == cl, ]

    # Calculate Euclidian distance between 
    # each point (row) and cluster center.
    dist <- sqrt(rowSums((df_part - centers[cl, ]) ** 2))

    # Calculate SD for each column (i.e. SD along each axis)
    sd_s <- apply(df_part - centers[cl, ], 2, sd)
    names(sd_s) <- paste("sd_", colnames(df_part), sep = "")

    res_part <- c(cluster = cl, total_sd = sd(dist), sd_s)
    res_sd <- rbind(res_sd, res_part)
}

res_sd <- as.data.frame(res_sd)
rownames(res_sd) <- res_sd$cluster
```


#Print standard-devations, and centers of each cluster
```{r}
res_sd$sd_Dim.1
```

```{r}
res_sd$sd_Dim.2
```

```{r}
print(k2_1$centers)

```


# Create a dataframe out of the clusters centers and standard deviations
```{r}
cluster_df2 <- data.frame("Cluster"=c("Cluster 1", "Cluster 2", "Cluster 3"),
                  "Dim1"=c(-0.1112676   ,
                           1.7238843      ,
                         1.5578184  ),
                  "Dim2"=c(-0.0398334,
                           -1.5995440,
                            1.6175377),
                  "Sd1"=c(0.6821503   ,
                          0.4866247    ,
                          1.8422183 ),
                  "Sd2"=c(0.6064306  ,
                         0.4545061   ,
                         1.8975165))
```




# Plot clusters by their centers and standard devations
```{r}
plot_1 <- ggplot(cluster_df2, aes(x=Dim1, y=Dim2,color=Cluster)) + 
  geom_vline(xintercept = 0)  + geom_hline(yintercept = 0) +
  geom_point() + geom_ellipse(aes(x0 = Dim1, y0 = Dim2, a = Sd1, b = Sd2, angle = 0)) +
  geom_label_repel(aes(label = Cluster),box.padding   = 0.01, 
                   size=3, point.padding = 10,
                   segment.color = 'grey50', label.size = 0.1, max.overlaps = 10) +
  annotate(geom="text", x= 1.4, y=1.65, label="Quantitative studies following gentrifiers; 
           gentrifiers moving to the city",
           color="#333333", size=3.5) +
  annotate(geom="text", x=1.8, y= -2, label="State-led gentrification studies following displacees",
           color="#333333", size=3.5) +
  annotate(geom="text", x=0.9, y=0.25, label="Quantitative  studies following gentrifiers; 
           gentrifiers moving within the city",
           color="#333333", size=3.5) +
  annotate(geom="text", x= -0.637, y= - 0.75, label="Qualitative 
           urban restructuring studies",
           color="#333333", size=3.5) +
  theme_classic() + theme(legend.position = "none")+
  labs(caption = "MCA out of 47 articles")# + ggsave("clusterplot5.png")




plot_1 <- plot_1 + expand_limits(x = c(-2, 3.5), y = c(-2.2, 2.2))

plot_1

```

# Plot Observation coordinate plot
```{r}


mca1_obs_df$label <-  rownames(mca1_obs_df)


plot_3 <-  ggplot(mca1_obs_df, aes(x=Dim.1, y=Dim.2)) + 
  geom_point(position = position_dodge(width = 0.5 )) + 
  geom_vline(xintercept = 0)  + geom_hline(yintercept = 0) +
  geom_label_repel(aes(label = label),box.padding   = 0.2, 
                   size=3, point.padding = 0.2,
                   segment.color = 'grey50', label.size = 0.1, max.overlaps = 15) +
  theme_classic() + theme(legend.position = "none")+
  labs(caption = "MCA out of 48 articles") #+   ggsave("mca1plot3.svg" )
plot_3


plot_3 <- plot_3 + expand_limits(x = c(-2, 3.5), y = c(-2.2, 2.2))

plot_1


```


